A Test of the Frequency Independence Assumption of Power System Coefficients used in Geomagnetically Induced Current Estimates

### 2019-07-31 paper.tex
New fig filenames

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_raw_All_20060805.pdf}
  \caption{(Top) Geomagnetic field measured at the Memanbetsu Magnetic Observatory (MMB). (Middle) Geoelectric field measured at the Memanbetsu Magnetic Observatory (MMB). (Bottom) GIC measurements at Memanbetsu substation. The subscripts $x$ and $y$ correspond to Geographic North and East, respectively, the date labels are for Universal Time, and the average have been subtracted from each time series.}
  \label{sample}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_predictions-MeanModel-2006-08-06.pdf}
  \caption{Out-of-sample model predictions (top) and predictions errors for each model in a selected 1-day interval. Note that the scales for the error time series differ from that for the top panel so that the error amplitudes are scaled up by a factor of 2.}
  \label{predictions}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_SN-options-1.pdf}
  \caption{Out-of-sample signal-to-noise (signal to prediction error) ratios at the evaluation frequencies for the four models.}
  \label{SN}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_aobo_histograms-options-1.pdf}
  \caption{Distribution of coefficients in Model~1. Each set of coefficients was computed 35 times using one day of 1-second cadence data. The circle or dot on the horizontal axis indicates the average of a histogram: $a_o$ = 73 A/(V/km) and $b_o$ = -72 A/(V/km).}
  \label{histogram}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_Z-options-1.pdf}
  \caption{Frequency domain transfer functions for the coefficients in Models 1, 2, and 4. The frequency domain transfer functions for $a_o$ and $b_o$ in Model~1 are constant and equal to $a_o$ and $b_o$.}
  \label{Z}
  %\end{figure}

@@

  %\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_Phi-options-1.pdf}
  \caption{Frequency domain phase values for the coefficients in Models 1, 2, and 4. The phase for $a_o$ and $b_o$ are constant and either 0$^{\circ}$ or 180$^{\circ}$ depending on the sign of their value, with positive values having a phase of 0$^{\circ}$.}
  \label{Phi}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_Z_MT-options-1.pdf}
  \caption{Frequency domain transfer functions for the $\mathbf{Z}$ coefficients used in Model~3.}
  \label{Z_MT}
  %\end{figure}

@@

  %\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_Phi_MT-options-1.pdf}
  \caption{Frequency domain phase values for the $\mathbf{Z}$ coefficients used in Model~3.}
  \label{Phi_MT}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_raw_All_20060805-v1.pdf}
  \caption{(Top) Geomagnetic field measured at the Memanbetsu Magnetic Observatory (MMB). (Middle) Geoelectric field measured at the Memanbetsu Magnetic Observatory (MMB). (Bottom) GIC measurements at Memanbetsu substation. The subscripts $x$ and $y$ correspond to Geographic North and East, respectively, the date labels are for Universal Time, and the average have been subtracted from each time series.}
  \label{sample}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_GIC_predictions-MeanModel-2006-08-06-v0-o0.pdf}
  \caption{Out-of-sample model predictions (top) and predictions errors for each model in a selected 1-day interval. Note that the scales for the error time series differ from that for the top panel so that the error amplitudes are scaled up by a factor of 2.}
  \label{predictions}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_SN-options-1-v0-o0.pdf}
  \caption{Out-of-sample signal-to-noise (signal to prediction error) ratios at the evaluation frequencies for the four models.}
  \label{SN}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_aobo_histograms-options-1-v0-o0.pdf}
  \caption{Distribution of coefficients in Model~1. Each set of coefficients was computed 35 times using one day of 1-second cadence data. The circle or dot on the horizontal axis indicates the average of a histogram: $a_o$ = 73 A/(V/km) and $b_o$ = -72 A/(V/km).}
  \label{histogram}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_Z-options-1-v0-o0.pdf}
  \caption{Frequency domain transfer functions for the coefficients in Models 1, 2, and 4. The frequency domain transfer functions for $a_o$ and $b_o$ in Model~1 are constant and equal to $a_o$ and $b_o$.}
  \label{Z}
  %\end{figure}

@@

  %\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_Phi-options-1-v1-o0.pdf}
  \caption{Frequency domain phase values for the coefficients in Models 1, 2, and 4. The phase for $a_o$ and $b_o$ are constant and either 0$^{\circ}$ or 180$^{\circ}$ depending on the sign of their value, with positive values having a phase of 0$^{\circ}$.}
  \label{Phi}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_Z_MT-options-1-v0-o0.pdf}
  \caption{Frequency domain transfer functions for the $\mathbf{Z}$ coefficients used in Model~3.}
  \label{Z_MT}
  %\end{figure}

@@

  %\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_model_summary_Phi_MT-options-1-v1-o1.pdf}
  \caption{Frequency domain phase values for the $\mathbf{Z}$ coefficients used in Model~3.}
  \label{Phi_MT}
\end{figure}
